### 2021-01-25 background.tex
first introduction fit

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance. For example, L Bao et al. \cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. His first experiment used a small set of apps (10 pairs B/M) to be run for different periods to compare how much time the tools needed to achieve the maximum coverage possible and to identify the sensitive APIs accessed. This study showed that the coverage and accuracy of the testing tool have a negative correlation. That is, improving the performance of code coverage might not directly contribute to the performance of detecting malware. The second experiment used a set of 102 pairs of apps that were executed for just one minute. The goal of this experiment was to compare a bigger number of apps and the number of sensitive APIs accessed by each tool in a small time.

>>>>

L Bao et al. \cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior. However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.

### 2021-01-25 introduction.tex
first introduction fit

The use of mobile devices such as smartphones and tablets continues increasing its importance in our daily lives. It is estimated that two-thirds of people on the planet use mobile technologies \cite{Comscore}, and in this context, Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}. Security issues in application consumption (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}. Currently, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using automated tools for testing. These tools, explore apps behaviors based on their sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources, which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory power of each testing tool used to compose the sandbox rules.

Previous research studies \cite{bao2018mining} have investigated the effectiveness of mining sandboxes, using automated testing tools, comparing the performance of each tool to mine sandboxes, as well as if the combination of one or more of them could lead to performance improvements. This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior. However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.

Jamrozik et al. \cite{jamrozik2016mining} discuss that dynamic analysis exceeds static analysis on mining Android sandboxes domain, although your point of view has not been validated empirically, and there was no effective discussion about the possibility of combination of both proposals, even though in some preliminary results, we found that some analysis static algorithms can complements analysis dynamic performance in mining sandbox task.

@@

%% Our objective is to assist researchers and practitioners in reproducing research studies in this field. Altogether, the main contribution of \droidxp  is to facilitate the reproduction of empirical studies, and allowing
%% researchers to integrate test case generation tools ratify.}

>>>>

Almost two-thirds of the world population use mobile technologies \cite{Comscore}, and Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}. Security issues in (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}. For instance, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using automated tools for testing. These tools, explore apps behaviors based on their sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources, which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.

A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}. The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain. However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals. Moreover, Bao et al. \cite{bao2018mining} present an empirical study comparing different dynamic analysis tools for mining sandboxes, that leverage DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comparing a benign and a malign version of an App), and collect information needed to mine sandboxes. Although the authors report an efficient in identifying 70\% of the malware in this specific dataset, part of this result is due to an internal static analysis algorithm of DroidFax, which might improve the performance of the dynamic analysis tools for mining sandboxes, introducing a possible threat to the work.

@@
